\sc Factorization Algebras and Factorization Homology on Stratified Spaces

### 2024-09-13 sections/4additivity.tex
Outline of additivity.

\begin{proof}
    Following \cite[\S.2.2.5]{lurie_ha} the tensor product of $\infty$-operads is defined through a universal property. Namely, we define a bifunctor of $\infty$-operads to be a map $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}$ such that:
    %
    \begin{enumerate}
        \item The diagram
        %
        \begin{equation}
            \begin{tikzcd}
                \mathscr{O}_1 \times \mathscr{O}_2 \arrow[r, "f"] \arrow[d] & \mathscr{O} \arrow[d] \\
                \mathsf{Fin}_* \times \mathsf{Fin}_* \arrow[r, "\wedge"] & \mathsf{Fin}_*
            \end{tikzcd}
        \end{equation}
        %
        commutes, and
        \item $f$ sends pairs of inert morphisms in $\mathscr{O}_1$ and $\mathscr{O}_2$ to inert morphisms in $\mathscr{O}$.
    \end{enumerate}
    %
    We denote the full $\infty$-subcategory of $\mathsf{Fun}_{\mathsf{Fin}_*}(\mathscr{O}_1 \times \mathscr{O}_2, \mathscr{O})$ consisting of the bifunctors of $\infty$-operads by $\mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O})$. The universal property of the tensor product is then that it is the $\infty$-operad $\mathscr{O}_1 \otimes \mathscr{O}_2$ together with a bifunctor of $\infty$-operads $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}_1 \otimes \mathscr{O}_2$ such that composition with $f$ determines an equivalence
    %
    \begin{equation}
        \alg{\mathscr{O}_1 \otimes \mathscr{O}_2} (\mathscr{O}) \xrightarrow{\ \ \simeq \ \ } \mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O}),
    \end{equation}
    %
    for every $\infty$-operad $\mathscr{O}$\footnote{More details about the construction, its existence, and the fact that it captures a nontrivial concept can be found in the provided reference.}.

@@

    The equivalence of $\infty$-operads $\disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N}$ implies an equivalence at the level of $\alg{\disk_{/M}}$, which together with \Cref{thm:disk_alg=lcfa} gives rise to the equivalence of factorization algebras in the theorem statement. That this is related to the functor $\bar{\pi}$ can be seen by inspection of the objects and morphisms.
\end{proof}

@@

\begin{example}
    We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{thm:additivity_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:
    %
    \begin{proposition}\label{prop:dunn_additivity}
        There is an equivalence of $\infty$-categories
        %
        \begin{equation}
            \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)).
        \end{equation}
    \end{proposition}
\end{example}

>>>>

{\color{red} The following lemmas are just an outline for a possible proof following Lurie as an example}

\begin{lemma}\label{lem:slicing_disk_functor}
    The construction of $\disk_{/M}$ elevates to a functor
    %
    \begin{equation}
        \disk_{/-}: \mfld \xrightarrow{\ \ \ \ \ } \mathscr{O}\mathsf{p}_{\infty}.
    \end{equation}
\end{lemma}

\begin{proof}
    .....
\end{proof}

\begin{lemma}
    The functor $\disk_{/-}$ from \Cref{lem:slicing_disk_functor} factorizes as in the commutative diagram
    %
    \begin{equation}
        \begin{tikzcd}
            \mfld \arrow[rr, "\disk_{/-}"] \arrow[dr, "\mathsf{Entr}"'] & & \mathscr{O} \mathsf{p}_{\infty} \\
            & \cat \arrow[ur, "(-)^\sqcup ??"'] &
        \end{tikzcd}
    \end{equation}
\end{lemma}

\begin{proof}
    .....
\end{proof}

\begin{proof}[Proof of \Cref{thm:additivity_lc}]
    Following \cite[\S.2.2.5]{lurie_ha} the tensor product of $\infty$-operads is defined through a universal property. Namely, we define a bifunctor of $\infty$-operads to be a map $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}$ such that:
    %
    \begin{enumerate}
        \item The diagram
        %
        \begin{equation}
            \begin{tikzcd}
                \mathscr{O}_1 \times \mathscr{O}_2 \arrow[r, "f"] \arrow[d] & \mathscr{O} \arrow[d] \\
                \mathsf{Fin}_* \times \mathsf{Fin}_* \arrow[r, "\wedge"] & \mathsf{Fin}_*
            \end{tikzcd}
        \end{equation}
        %
        commutes, and
        \item $f$ sends pairs of inert morphisms in $\mathscr{O}_1$ and $\mathscr{O}_2$ to inert morphisms in $\mathscr{O}$.
    \end{enumerate}
    %
    We denote the full $\infty$-subcategory of $\mathsf{Fun}_{\mathsf{Fin}_*}(\mathscr{O}_1 \times \mathscr{O}_2, \mathscr{O})$ consisting of the bifunctors of $\infty$-operads by $\mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O})$. The universal property of the tensor product is then that it is the $\infty$-operad $\mathscr{O}_1 \otimes \mathscr{O}_2$ together with a bifunctor of $\infty$-operads $f: \mathscr{O}_1 \times \mathscr{O}_2 \xrightarrow{} \mathscr{O}_1 \otimes \mathscr{O}_2$ such that composition with $f$ determines an equivalence
    %
    \begin{equation}
        \alg{\mathscr{O}_1 \otimes \mathscr{O}_2} (\mathscr{O}) \xrightarrow{\ \ \simeq \ \ } \mathsf{BiFunc}(\mathscr{O}_1, \mathscr{O}_2; \mathscr{O}),
    \end{equation}
    %
    for every $\infty$-operad $\mathscr{O}$\footnote{More details about the construction, its existence, and the fact that it captures a nontrivial concept can be found in the provided reference.}.

@@

    The equivalence of $\infty$-operads $\disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N}$ implies an equivalence at the level of $\alg{\disk_{/M}} (\catC)$, which together with \Cref{thm:disk_alg=lcfa} gives rise to the equivalence of factorization algebras in the theorem statement. That this is related to the functor $\bar{\pi}$ can be seen by inspection of the objects and morphisms.
\end{proof}

@@

\begin{example}
    We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \Cref{thm:additivity_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:
    %
    \begin{corollary}\label{prop:dunn_additivity}
        There is an equivalence of $\infty$-categories
        %
        \begin{equation}
            \alg{\mathbb{E}_{n + m}} (\catC) \xrightarrow{\ \ \simeq \ \ } \alg{\mathbb{E}_n} (\alg{\mathbb{E}_m} (\catC)).
        \end{equation}
    \end{corollary}
\end{example}
